```{r, echo=TRUE}

random_vars<-readRDS("C:/Users/mouni/Downloads/Causal_Data_Science_Data/Causal_Data_Science_Data/random_vars.rds")
View(random_vars)
```
1.
```{r, echo=TRUE}

mean(random_vars$age)
mean(random_vars$income)
var(random_vars)
var(random_vars$income)
sd(random_vars$age)
sd(random_vars$income)
```
2.
Standard deviation is the square root of the variance and provides a measure of the average distance of data points from the mean.
Comparing standard deviations makes sense when the variables are on similar scales. Higher standard deviations indicate greater variability.

3.
```{r, echo=TRUE}
cov(random_vars)
cor(random_vars)
```
4.Correlation is often easier to interpret as it is scaled between -1 and 1, making it independent of the scale of the variables. It indicates the strength and direction of a linear relationship.
Covariance is in the units of the product of the two variables, making it sensitive to the scales.

5.
```{r, echo=TRUE}
aggregate(income ~ (age<=18), data=random_vars,FUN=mean)
aggregate(income ~ (age>=18 & age<=65), data=random_vars,FUN=mean)
aggregate(income ~ (age>=65), data=random_vars,FUN=mean)

```



