---
title: "Directed Acyclic Graphs"
---

::: callout-note
:::

1.)
```{r, echo=TRUE}
customer_data<-readRDS("C:/Users/mouni/Downloads/Causal_Data_Science_Data/Causal_Data_Science_Data/customer_sat.rds")

library(dagitty)

dag <- dagitty('dag {
  location -> parking_spot
  parking_spot -> sales
}')
coords = list(x = c(Y = 3, Z = 2, X = 1),
                y = c(Y = 0, Z = 0, X = 0))
plot(dag)

```
2.)
```{r, echo=TRUE}

customer_data<-readRDS("C:/Users/mouni/Downloads/Causal_Data_Science_Data/Causal_Data_Science_Data/customer_sat.rds")

       
model1<-lm(satisfaction~follow_ups,data=customer_data)
summary(model1)

model2<-lm(satisfaction~follow_ups+subscription,data=customer_data)
summary(model2)

coef_comp<-cbind(T1=coef(model1),T2=coef(model2))
print(coef_comp)
```

3.)
Comparison:
Intercept:
In Model 1, the intercept is 78.8860.
In Model 2, when accounting for subscription, the intercept decreases significantly to 26.7667.

follow_ups:
In Model 1, the coefficient for follow_ups is -3.3093.
In Model 2, when accounting for subscription, the coefficient for follow_ups becomes 2.1944.

subscription:
The coefficients for both subscription levels(premium and premium+) are positive and statistically significant.

The significant decrease in the intercept possibly says that, on average, satisfaction is lower when considering the impact of subscription levels.

The change in the coefficient for follow_ups suggests that the relationship between follow-up calls and satisfaction is positive as it changed from (-3.3093 to 2.1944) when accounting for subscription levels. This could indicate that the effect of follow-up calls on satisfaction depends on the subscription level.

Higher subscription levels, Premium and Premium+, are associated with significantly higher satisfaction. The decrease in the intercept suggests that the baseline satisfaction is lower when considering subscription levels.


4.)
```{r, echo=TRUE}

library(dagitty)
library(tidyverse)
data <- dagitty('dag {
  follow_ups -> satisfaction
  subscription -> follow_ups
  subscription -> satisfaction
}')

  coordinates(dag) <- list(x = c(subscription = 3, follow_ups = 2, satisfaction = 1), y = c(subscription = 0, follow_ups = 1, satisfaction = 0))
  #label <- data.frame(x = c(2, 2, 3), y = c(1, 2, 2), label = c("b1", "b2", "b3"))
  plot(data, main = "Directed Acyclic Graph (DAG) for Relationship Analysis")
# Plot DAG
library(ggdag)

```
  
  
  
  
data<-readRDS("C:/Users/mouni/Downloads/Causal_Data_Science_Data/Causal_Data_Science_Data/customer_sat.rds")
n <- 1e+03

# draw and create variables with specific dependencies
subscription <- rnorm(n)
follow_ups <- rnorm(n) 
satisfaction <- rnorm(n)

# rescale to realistic values
satisfaction <- sample(20:80,1) + scales::rescale(satisfaction, to = c(0, 80))
follow_ups <- scales::rescale(follow_ups, to = c(0, 10))
subscription <- factor(subscription, labels = c("Premium+", "Premium"))

# create tibble
df <- tibble(
  satisfaction,
  follow_ups,
  subscription
)

# Not conditioning on education
simps_not_cond <- ggplot(df, aes(x = follow_ups, y = satisfaction)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F)

# Conditioning on education  
simps_cond <- ggplot(df, aes(x = follow_ups, y = satisfaction, color = subscription)) +
  geom_point(alpha = .8) +
  stat_smooth(method = "lm", se = F) +
  theme(legend.position = "right")

# Plot both plots
simps_not_cond
simps_cond
