---
title: "Difference-in-Differences"
---

::: callout-note
:::

1.)
```{r, echo=TRUE}
hospdd_data<-readRDS("C:/Users/mouni/Downloads/Causal_Data_Science_Data/Causal_Data_Science_Data/hospdd.rds")

df_treated <- hospdd_data %>%
  filter(procedure == 1) %>%
  group_by(month) %>%
  summarise(mean_satisfaction_treated = mean(satis))
print(df_treated)

df_control <- hospdd_data %>%
  filter(procedure == 0) %>%
  group_by(month) %>%
  summarise(mean_satisfaction_control = mean(satis))
print(df_control)
```
2.)
```{r, echo=TRUE}
reg_model_1 <- lm(satis~procedure*month+hospital,data=hospdd_data)
summary(reg_model_1)

reg_model_2 <-lm(satis~procedure*as.factor(month)+as.factor(hospital),data=hospdd_data)
summary(reg_model_2)
```

Choosing the model specification depends on the characteristics and assumptions of model data.The as.factor method gives the regressor value for each hospital i.e (46) hospitals for each month but in the case of normal method there are only 2 coefficients.The first method is best for continuous data and the second method for categorical data.Considering months and hospital as numeric,we assume it be a linear relationship with satisfaction,whereas considering them as factors leads to non-linear relationship.




