---
title: "Instrumental Variables"
---

::: callout-note
:::
1.)
```{r, echo=TRUE}

rand_enc_data<-readRDS("C:/Users/mouni/Downloads/Causal_Data_Science_Data/Causal_Data_Science_Data/rand_enc.rds")
library(dagitty)
dag <- dagitty('dag {
  rand_enc->used_ftr
  used_ftr->time_spent
}')
coords = list(x = c(Y = 3, Z = 2, X = 1),
                y = c(Y = 0, Z = 0, X = 0))
plot(dag)
```

2.)
The naive  estimate would be the simple comparison between average time spent by users who were encouraged (rand_enc=1) and those who were not (rand_enc=0).This would be biased due to potential unobserved confounders.
```{r, echo=TRUE}

library("dplyr")
df <- rand_enc_data %>%  group_by (rand_enc) %>% 
summarize(avg_time_spent=mean(time_spent))
print(df)

lm_naive<-lm(time_spent~used_ftr,data=rand_enc_data)
summary(lm_naive)
```
3.)
```{r, echo=TRUE}

com_ins<-ggplot(rand_enc_data, aes(x = rand_enc,y=used_ftr)) +
  geom_point(alpha=0.8) +
  stat_smooth(method="lm",se=F)
  labs(title = "Distribution of Encouragement Variable",
       x = "Encouragement",
       y = "Treat")
com_outcome<-ggplot(rand_enc_data, aes(x = rand_enc,y=time_spent)) +
  geom_point(alpha=0.8) +
  stat_smooth(method="lm",se=F)
  labs(title = "Distribution of Encouragement Variable",
       x = "Encouragement",
       y = "outcome")
com_treat<-ggplot(rand_enc_data, aes(x = used_ftr,y=time_spent)) +
  geom_point(alpha=0.8) +
  stat_smooth(method="lm",se=F)
  labs(title = "Distribution of Encouragement Variable",
       x = "Treat",
       y = "Outcome")
com_ins
com_outcome
com_treat
# Check correlations: Examine correlations between variables of interest
cor(rand_enc_data$rand_enc, rand_enc_data$time_spent)
cor(rand_enc_data$rand_enc, rand_enc_data$used_ftr)
cor(rand_enc_data$used_ftr,rand_enc_data$time_spent)
```
4.)
```{r, echo=TRUE}

#1st method

first_stage <-lm(used_ftr~rand_enc,data=rand_enc_data)
summary(first_stage)
second_stage <-lm(rand_enc_data$time_spent~first_stage$fitted.values)
summary(second_stage)

#2nd method
library(estimatr)
model <-iv_robust(time_spent~used_ftr|rand_enc,data=rand_enc_data)
summary(model)
```
There is significant difference between IV estimate and naive bias estimate and thus naive estimate is biased and that used_ftr coefficient is higher than expected and thus it is an upward bias.